---
title: "stGOF Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

The `stGOF` is designed to Performs the smooth test for the one-sample goodness-of-fit problem as described by *Rayner et al*.(2009). Both simple and composite null hypotheses can be tested. The maximum likelihood (`MLE`) and the method of moments (`MME`) methods for nuisance parameter estimation are implemented. Function returns the score statistics of Smooth test result.

The goal of `stGOF` package is to return the smooth test result as descriped in ***"Smooth Tests of Goodness of Fit Using R"*** book by D. *John Best, J. C. W. Rayner, and Olivier Thas*.smooth tests and data-driven smooth tests of goodness of fit can be performed for several distributions. The package also contains functions for the construction of sets of orthonormal polynomials.

## Installation

You can install the development version of stGOF from [GitHub](https://github.com/krakla/stGOF) with:

`install.packages("devtools")`

`devtools::install_github("krakla/stGOF")`

## Including Plots

You can also embed plots, for example:

## Example

This is a basic example which shows you how to calculate smooth test PCB data which follows the normal distribution and using MLE as an estimation method

```{r}
library(stGOF)
stGOF(PRG ~ unif, PRG, order = 4, method = "MLE")
```

In addition, there are several functions to calculate the MLE, MME estimators. Also, there are functions can be used to construct of sets of orthonormal polynomials. For example, here is the MLE estimator for pulse data.

`norm.MLE(pulse)`

#### Other examples

```{r}
stGOF(PCB ~ norm, PCB, order = 4, method = "MLE")
```
```{r}
stGOF(PCB ~ norm, PCB, order = 6, method = "MLE")
```

```{r}
stGOF(PCB ~ norm, PCB, order = 7, method = "MLE")
```

```{r}
stGOF(PCB ~ norm, PCB, order = 6, method = "MLE", B = 1000, rescale = TRUE)
```

```{r}
stGOF(PCB ~ norm, PCB, method = "MLE", B = 1000, max.order = 7, horizon="order", criterion="AIC")
```

```{r}
stGOF(PCB ~ norm, PCB, method = "MME", B = 1000, max.order = 7, horizon="subset", criterion="BIC")
```

