---
title: "stGOF Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

The stGOF is designed to Performs the smooth test for the one-sample goodness-of-fit problem as described by Rayner et al.(2009). Both simple and composite null hypotheses can be tested. The maximum likelihood (MLE) and the method of moments (MME) methods for nuisance parameter estimation are implemented. Function returns the score statistics of Smooth test result.

The goal of stGOF package is to return the smooth test result as descriped in **_"Smooth Tests of Goodness of Fit Using R"_** book by D. John Best, J. C. W. Rayner, and Olivier Thas.smooth tests and data-driven smooth tests of goodness of fit can be performed for several distributions. The package also contains functions for the construction of sets of orthonormal polynomials.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
